Accelerating adaptive ultrasound algorithms using graphics processing units \vspace{0.5cm}

### 2014-01-12 ThesisJP/Introduction/introduction.tex
Writing summary of paper 3.

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}\\\\
In the third paper we study the shift-invariant property of an imaging system based on the Capon beamformer. As mentioned, shift-invariant imaging is essential if the method is ever to be adopted. The paper was written based on observations of aliasing artifacts when imaging bright point scatterers \textit{in vitro} and in simulations. In earlier work on Capon beamforming for medical ultrasound imaging the real-time nature of ultrasound imaging has been ignored, and a large degree of oversampling has often been applied in simulations.

>>>>

\subsection{Paper III}
\textbf{Capon Beamforming and Moving Objects - An Analysis of Lateral Shift-Invariance}\\
\textbf{J.\:P.\:\AA{}sen}, A.\:Austeng and S.\:Holm\\
{\it IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control, submitted.}\\\\
In the third paper we study the shift-invariant property of an imaging system based on the Capon beamformer. As mentioned, shift-invariant imaging is essential if the method is ever to be adopted. The paper was written based on observations of aliasing artifacts when imaging bright point scatterers \textit{in vitro} and in simulations. The points were twinkling like stars in the sky. In earlier work on Capon beamforming for medical ultrasound imaging the real-time nature of ultrasound imaging has been ignored, and a large degree of oversampling on transmit has often been applied without comments. Oversampling on transmit is not an option if the imaging modality is used to image rapidly varying objects.

In \textbf{Paper III} we investigate how the Capon beamforming achieves its super resolution, and how this makes it highly sensitive to differences between the assumed steering vector and the signal propagation vector. Earlier work, focusing on single images, has typically referred to this effect as speed-of-sound errors, but it also comes naturally into play when objects moves from frame to frame and the beam density is insufficient. With a narrow band and farfield model we show that 25 times oversampling is required to obtain the same lateral gain variations as with \nom{DAS}{Delay-and-sum beamforming} beamforming. These calculations are done based on typical parameters for the Capon beamformer. For
